---
title: "p8105_hw5_rl3411"
author: "rl3411"
date: "2023-11-09"
output: github_document
---

```{r}
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(
    echo = TRUE,
    warning = FALSE,
    fig.width = 8, 
  fig.height = 6,
  out.width = "100%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
hom_data = read_csv("data/homicide-data.csv")
```

Describe raw data!

```{r}
hom_data = hom_data |> 
  mutate(city_state = paste(city, state, sep =", "))
```

# Problem 2

### Create and tidy dataset

```{r, message = F}
study = 
  tibble(file_name = list.files(path = "data", 
                                pattern = "^[a-z]{3}_\\d{2}\\.csv$", 
                                full.names = TRUE)) |> 
  mutate(value = map(file_name, read_csv)) |> 
  unnest(value) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "obs"
  ) |> 
  mutate(week = str_sub(week, 6, 6),
         file_name = str_sub(file_name, 6, 11),
         file_name = str_replace_all(file_name, c("con"= "control", "exp" = "experimental"))) |> 
  rename(arm_ID = file_name)
```

### Spaghetti plot: observations on each subject over time

```{r, message = F}
study |> 
  mutate(arm = case_when(
    str_detect(arm_ID, "^control") ~ "control",
    str_detect(arm_ID, "^experimental") ~ "experimental")) |> 
  ggplot(aes(x = week, y = obs, group = arm_ID, color = arm_ID)) + 
  geom_line() +
  geom_smooth(aes(group = arm, color = factor(arm)), se = F) +
  labs(title = "Observations on each subject over 8 weeks")
```

From this plot, we can see that the observational values for subjects in the experimental arm increases through the 8-week period while those in the control arm remain around 1.2 units. This suggests that the treatment/intervention might be causing an effect, resulting in higher values among the experimental group.

# Problem 3


### Generating dataset of samples

```{r}
set.seed(828)

mu_sample = function(mu, n = 30, sd = 5){
  x_vec = rnorm(n = n, mean = mu, sd = sd)
  sim_result = t.test(x_vec, mu = 0, alternative = "two.sided", conf.level = 0.95) |> 
    broom::tidy() |> 
    select(estimate, p.value)
}

sim_result_df = 
  expand_grid(
    mu = c(0,1,2,3,4,5,6),
    iter = 1:5000
  ) |> 
  mutate(estimate_df = map(mu, mu_sample)) |> 
  unnest(estimate_df) |> 
  mutate(power = p.value < 0.05)
```

### Investigating the power of the test

```{r}
sim_result_df |>  
  group_by(mu) |>  
  summarize(prop = mean(power)) |> 
  ggplot(aes(x = factor(mu), y = prop)) +
  geom_bar(stat = "identity") +
  labs(title = "Proportion of times the null was rejected for each mu",
       x = "mu",
       y = "Power")
```

Describe the association between effect size and power.
From this plot, we can see that the power increases as the true value of $\mu$ increases. 

```{r}
overlay_data = sim_result_df |> 
  filter(power == TRUE) |> 
  select(mu, estimate) |> 
  group_by(mu) |>  
  summarize(mean_mu = mean(estimate))

sim_result_df |>  
  group_by(mu) |>  
  summarize(mean_mu = mean(estimate)) |> 
  ggplot(aes(x = (mu), y = mean_mu)) +
  geom_line(color = "orange") +
  geom_point(color = "orange") +
  geom_line(data = overlay_data, color = "blue") +
  geom_point(data = overlay_data, color = "blue") +
  scale_x_discrete(limits = seq(0,6,1)) +
  scale_y_discrete(limits = seq(0,6,1)) +
  labs(title = "Average estimate of mu hat vs true mu",
       x = "true mu",
       y = "Average estimate of mu hat")
```




















